The Astropy Project

### 2017-11-03 main.tex
Update on Overleaf.

\inlinecomment{David S.}

The \package{Constants} package provides useful physical constants as quantities.  The package was described in \cite{astropy}.  \package{Constants} now include their own version to track when their values are adjusted.

>>>>

%David S.

The \package{Constants} package provides a selection of physical and astronomical
constants as quantities.  A brief description was given in \cite{astropy}. 
For version 2.0, constants have been organized into modules for specific versions.
Physical constants include \texttt{codata2014} \citep{codata2014}
and \texttt{codata2010} versions. Astronomical constants are organized 
into \texttt{iau2015} and 
\texttt{iau2012} modules to roughly indicate their sources.
The \texttt{codata2014} and \texttt{iau2015} versions are combined 
into the default \texttt{astropyconst20}
version. For astropy v1.3 and earlier, the \texttt{astropyconst13} 
namespace is available;
however when using previous versions of the constants, 
\package{Constants} should be used
directly, since  \package{astropy.units} will be initialized to the 
\texttt{astropyconst20} versions.

Astronomers using \package{Constants} should take particular note of the
constants provided for Earth, Jupiter and the Sun. Following IAU 2015 
Resolution B3 \citep{iau2015b3}, nominal
values are now given for mass parameters and radii. The nominal values 
will not change even as ``current best estimates'' are updated.

\inlinecomment{DavidS: we'd like to build on this to allow use of a
context manager for selecting a version of constants. Here, or in the Future
section?}
